---
title: "Creating a Lesson Repo From Scratch"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating a Lesson Repo From Scratch}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(decampr)
```

## Using `decampr` to create a course repo from scratch

The first thing to do is to use `decampr::create_course_repo()` to clone Ines' basic course repository to your computer:

```r
decampr::create_course_repo()
```

This will clone the `course-starter-r` repo to your computer (by default, it saves it to your Desktop) and open up a new project with your cloned repo.

Make sure to rename it and save it as a new project. Also, use `use_github()` to add it to GitHub, so you can serve the repository up to both your webhost and mybinder.org.


## Adding a new chapter file.

We've got you covered. You can use `add_chapter()` to initialize a new chapter file and open it automatically.

Say I wanted to add a new `chapter6.md` to my course. I can use

```r
add_chapter("chapter6.md")
```

And this file will be created, along with the relevant YAML to get the course to work.

I can then start adding exercises using the `add_exercise()` function (see below).

## Adding an exercise to the end of your chapter

If you want to expand on your work, there is another convenience function called `add_exercise()`:

```r
add_exercise("chapter1.md", "01_10")
```

Which will add a new set of HTML exercise tags for your exercise to your `chapter1.md` file, and will open this file for further editing. Furthermore, the exercise, solution, and pre-exercise files will be open.

Note that if you already have a codeblock with that id, function will return an error, preventing you from overwriting the files.

## Editing Individual Exercises

The `open_exercise()` function will open the exercises in Rstudio with a particular_id. For example, if I wanted to edit the `03_03` exercise, solutions, and prexercise code (which would be `exercises/exc_03_03.R`, `exercises/solution_03_03.R` and `exercises/preexercise_03_03.R`), I could use:

```r
open_exercise("03_03")
```

And edit windows for each of these files would pop up.


## TODO: add_multiple_choice()

Coming soon!

## TODO: add_slides()

Coming soon!
